Order is half of life -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-12-16 paper/paper-mainfile.tex
comment intro
update TO=GBFS and PO=WA*  -- unknown weights

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{xcolor}
\usepackage{booktabs} 
% \usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb} 
\usepackage{mathbbol}
\usepackage{tikz}
\usetikzlibrary{aiplans}

@@

\begin{document}
\input{00--macro.tex}
\maketitle

@@

\section{Introduction}
\input{01--intro.tex}
Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound. HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks. A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications. If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.

@@

\section{Hierarchical Planning Formalism}
\input{02--htn.tex}

\section{Linearizing Grounded HTN Problems}
\input{03--linearization-ground.tex}

% The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other. This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.

% \subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }

% In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

% E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed. If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$. This is true for all possible tasks by simple induction over the decomposition process.

% Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.

% Specifically, let $\sigma$ be the set of parameters for the method. Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$. Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.

% Where a task accepts two parameters of the same type under different names, it is assumed those are different objects. For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects. % This is illustrated in Figure~\ref{CompoundPreEffForLifted}.

% This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$. The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded. Only one linearized lifted method per partially-ordered lifted method is produced.

% For a grounded method, there are no parameters in a task or method. Methods decompose to specific actions, actions have preconditions and effects on specific state variables. We can then use these to produce a linearized grounded method per grounded method.

% In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
% $f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
% \begin{align*}
% & \forall t \in T_P : \PreS(t) := \Pre(t) \\
% & \forall t \in T_P : \AddS(t) := \Add(t) \\
% & \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
% & \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
% & : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
% & \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
% & \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
% & m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
% \end{align*}

% \subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
% The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects. Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.

@@

% \begin{algorithm}[h]
% 	\caption{Calculation of linearized methods}
% 	\label{alg:Algorithm1}
% 	\KwData{$(F, T_P, T_C, \delta, M)$}
% 	\KwResult{$(F, T_P, T_C, \delta, M)$}

% 	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
% 	{
% 		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
% 		$G \gets \singlePrec$ \\
% 		\label{alg:StartBuildGraph}
% 		\For{a $\in$ F}{  
% 			\For{$t \in T_m$}{
% 				\For{$t' \in T_m$}{
% 					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
% 					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
% 					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
% 					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
% 				}
% 			} 
% 			\label{alg:EndBuildGraph}	
% 		}	
% 		\label{alg:StartCycleBreak}
% 		\While{$G$ has cycles in it}{
% 			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
% 		}
% 		\label{alg:EndCycleBreak}
% 		$\prec'$ = Any linearization of $G$ \\
% 		\label{alg:TopSort}
% 		$m' = (tasks(m), \prec', \alpha(t))$ \\
% 		$M' = M' \cup  \{m'\}$ \\

% 	}
% 	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
% \end{algorithm}

@@

 \begin{figure}[h]
 	\caption{Example of Desired Additional Orderings}
 	\label{fig:OrderingRules}
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{first}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

@@

		\end{subfigure}
	}  
	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{A}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of } 
			};

			\action{B}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of A} 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->,bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{C deletes a fact in preconditions of A  -- so A before C}	
		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{4.5cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{A}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of } 
			};

			\action{B}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of A} 
			};

			\path[every node/.style={font=\sffamily\small}]
			(B) edge [->, bend right] node [left]  {} (A);
			\end{tikzpicture}
			\caption{B adds a fact that C deletes -- so C before B}
		\end{subfigure}
	} 
\end{figure}

@@

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20}, on their default configuration. This turns problem into a classical planning problem (in RC model), uses Greedy best first search, FF heuristic by \cite{FF}, and visited lists. The visited lists use task sequence hashing, visited checking with task sequences, layer hashing, order pairs hashing, and GI-complete equivalence checking for partially-ordered task networks.

% \todo{visited checking with task sequences makes totally-ordered visited lists incomplete (with order) }

%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}

We also try that configuration with FF swapped for the Add heuristic by \cite{Add}.
%Filter by \cite{useClassicalHuristicICAPS18} and Landmark-cut by \cite{LM-Cut}. 
We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. For other planners, panda$_\pi$ with rc2(Add) is used for re-runs. We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). We test both Complex and Simple Inference for linearization. Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.

>>>>

%
% user import packages
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{paralist}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{varwidth}
\usepackage{xcolor}
\usepackage{booktabs} 
\usepackage[ruled, noend, linesnumbered]{algorithm2e}  
\usepackage{csquotes}
\usepackage{subcaption}
\usepackage{amssymb} 
\usepackage{tikz}
\usetikzlibrary{aiplans}

@@

\begin{document}

\maketitle

@@

\section{Introduction}
Hierarchical Task Network (HTN) planning is a hierarchical approach to planning. As defined by \cite{HTNSurvey},  %  and \cite{IntroGhallab},
tasks in HTN planning are either primitive, corresponding to an action that can be taken, or compound. HTN problems have a set of methods that specify how one might achieve a given compound task, by decomposing it into a set of sub-tasks. A compound task may even decompose into itself, either directly via a method, or indirectly via a sequence of method applications. If decomposition leads to a sequence of primitive tasks executable from the initial state, then this sequence of actions is a solution to the problem, also known as a \enquote{plan}.

@@

\section{Hierarchical Planning Formalism}
Hierarchical task network planning, also known as \textbf{HTN planning}, is one form of hierarchical planning. There are many formalisations for HTN planning. The following one borrows heavily from \cite{HTNSurvey} and \cite{Geier2011TIHTNDecidability}. HTN planning can be partially ordered, also known as POHTN planning, or totally ordered, otherwise known as TOHTN planning. TOHTN planning is a special case of POHTN planning.  % except with the initial task network replaced by a initial compound task.

A \textbf{Partially Ordered Hierarchical Planning}, also called POHTN, problem P = $(D, S_I, T_I)$
is defined over some domain $D$, 
has an initial state $S_I \in 2^F$, and 
has a initial compound task $T_I$. 
The closed world assumption also holds for HTN planning.

The domain is defined as \textbf{D} = $(F, T_P, T_C, \delta, M)$.
$F$ is the finite set of facts or state variables, $T_P$ is the finite set of all possible primitive task names, $T_C$ is the finite set of all possible compound task names, and
$\delta$ is a mapping from primitive task name to action. Actions in POHTN domain also have preconditions, adds, and delete effects.
$M$ is the finite set of decomposition methods. Each one maps a compound task name to a task network. If $m \in M$, then $m=(c, tn)$, where $c \in T_C$.

A task network \textbf{tn} = $(T, \singlePrec, \alpha)$ consists of
T, which is a finite set of task identifiers (ids); 
$\singlePrec$, which is a partial order over T; and
$\alpha$, which maps task ids $\in$ T to task names in $T_C$ and $T_P$.

% replacing t  (i.e. $tn_1 \rightarrow_{t,m} tn_2$)
A method $m = (c, tn_m)$ decomposes a task network $tn_1 = (T_1, \singlePrec_1, \alpha_1)$ into
a new task network $tn_2$ by replacing $t$, if and only if $t \in T_1$, $\alpha_1(t) = c$, and $\exists tn' = (T', \singlePrec' \alpha')$ with $tn' \cong tn_m$ and $T' \cap T = \emptyset$ and
\begin{align}
tn_2 :=     &((T_1 \setminus \{t\}) \cup T',    \singlePrec_1 \cup \singlePrec' \cup \singlePrec_X,        \alpha_1 \cup \alpha') \\
\singlePrec_X :=  &\{(t_1, t_2) \in T_1 \times T'  \mid  (t_1,t) \in \singlePrec_1 \} \cup \\
&\{(t_1, t_2) \in T' \times T_1 \mid (t, t_2) \in \singlePrec_1 \}  
\end{align}
In other words, the decomposition of a compound task results in it being removed from the task network and replaced by a copy of the method’s task network. The ordering constraints
on the removed task are inherited by its replacement tasks, as defined by $\singlePrec_X$.

A \textbf{solution} to an HTN problem is a task network $tn = (T, \prec, \alpha)$ if and only if
tn can be reached via decomposing $tn_I$, all tasks are primitive, ($\forall t \in T: \alpha(t) \in T_P$), and there exists a sequence $\langle t_1, t_2 ... t_n \rangle$ of the task ids in $T$ that agrees with $\prec$ such that the application of that sequence $\langle \alpha(t_1), \alpha(t_2) ... \alpha(t_n) \rangle$ in $S_I$ is executable.

%In other words, there is no goal state for hierarchical planning -- the goal is to find an decomposition of the initial task, then any executable refinement of the resulting decomposition. For any given hierarchical problem, it is trivial to enforce a goal state is met, by replacing the real initial task with a task whose only decomposition is to the real initial task and a primitive task ordered after it whose preconditions are equivalent to any \enquote{goal state} desired. Thus the fact that a goal state is not strictly required is not a restriction to the expressiveness of hierarchical planning. Whereas in classical planning, one only finds any executable sequence of actions to achieve a goal state, so HTN planning poses additional restrictions on which action sequences may be considered.

\textbf{Totally Ordered Hierarchical Planning}, also called TOHTN planning, is the same as partially ordered planning in all respects except the kind of task networks it allows.
%For both planning formalisms, a method $m$ maps a task $t$ to a task network \textbf{tn} = $(T, \prec, \alpha)$. TOHTN planning domains require that $\prec$ must specify a total order between task ids in $T$. This leads to a difference in expressiveness and decideability of TOHTN vs POHTN planning. POHTN planning is more expressive in general (both in terms of plan existence and in terms of computational complexity).

% As per \cite{LanguageClassificationPlanning}, if regarded from the standpoint of formal grammars, TOHTN planning is exactly as expressive as context free languages, whereas POHTN planning is strictly more expressive than context-free languages, and strictly less expressive than context-sensitive languages.
In terms of complexity classes, \cite{ErolHTNExpressivity} proved that POHTN planning is semi-decidable, whereas \cite{Alford2015TightHTNBounds} proved that, assuming arbitrary recursion, TOHTN planning is 2-EXPTIME-complete with variables, and EXPTIME-complete without.

\section{Inference of Preconditions and Effects}
The basic linearization process consists of inferring preconditions and effects for compound tasks, inferring additional orderings to the sub-tasks based on the preconditions and effects (inferred or \enquote{real} in the case of primitive tasks) of method sub-tasks. We first attempt to add them all, and then randomly remove orderings that conflict with the originally required orderings, or each other. This random removal of contradicting orderings is called \textbf{\textit{cycle-breaking}}.

\subsection{Simple Inference of Preconditions and Effects for Compound Tasks (For Lifted and Grounded Domain) }
In a lifted format, tasks and methods accept parameters, referring to any object of a specific type. Thus actions within a method have effects and preconditions that are symmetrical in terms of interactions within the method.

E.g.\ the task \textit{navigate(waypoint1, waypoint2)} will end up with some set of actions  $\bar{a}$ once decomposed. If you replace the passed parameters \textit{waypoint1} with \textit{waypoint3} and \textit{waypoint2} with \textit{waypoint4}, then \textit{navigate(waypoint3, waypoint4)} will have the same set of actions $\bar{a}$. This is true for all possible tasks by simple induction over the decomposition process.

Thus for each method, we can \enquote{ground} it in the standard way, but using an arbitrary object instead of all objects that exist in the domain.

Specifically, let $\sigma$ be the set of parameters for the method. Then for each parameter of the method, the set of typed objects $\omega$ has one object of the corresponding type, and $|\omega| = |\sigma|$. Then $\sigma(a, \omega)$, the groundings of a transition schema $a$ over $\omega$, corresponds to the ground method obtained by substituting $\sigma$ with the corresponding object of correct type taken from $\omega$.

Where a task accepts two parameters of the same type under different names, it is assumed those are different objects. For example, for \textit{Navigate(pt0, pt1, rover)}, \textit{pt0} and \textit{pt1} are assumed as different objects. % This is illustrated in Figure~\ref{CompoundPreEffForLifted}.

This allows actions to have some ground \enquote{predicate} \textit{at\_waypoint1}, rather than $at(?waypoint)$. The resulting \enquote{predicates} can be used to order the sub-tasks, while groundings for methods are discarded. Only one linearized lifted method per partially-ordered lifted method is produced.

For a grounded method, there are no parameters in a task or method. Methods decompose to specific actions, actions have preconditions and effects on specific state variables. We can then use these to produce a linearized grounded method per grounded method.

In summary, for a lifted domain, where a predicate $f$ accepts parameters $p_1, ..., p_n$, 
$f' = f(o_1, ..., o_n)$, where $o_1, ..., o_n$ are arbitrary objects of the appropriate type. For a grounded model, $f' = f$. The inferred preconditions and effects for a task are then defined as below:
\begin{align*}
& \forall t \in T_P : \PreS(t) := \Pre(t) \\
& \forall t \in T_P : \AddS(t) := \Add(t) \\
& \forall t \in T_P : \DelS(t) := \Del(t)  \\ %  \land
& \forall t \in T_C : \PreS(t) := \{f'  \mid  \exists m \in M  \\
& : m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \PreS(t') \}   \\
& \forall t \in T_C : \AddS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \AddS(t') \}   \\
& \forall t \in T_C : \DelS(t) := \{f'  \mid  \exists m \in M : \\
& m=(t,(T, \singlePrec, \alpha)) \forall t' \in T.  \forall  f \in \DelS(t') \}   \\ 
\end{align*}

\subsection{Complex Inference of Preconditions and Effects for Compound Tasks (for Grounded Domain) }
The work by~\cite{ConnyPreEstimation}, details a way to infer executability-relaxed preconditions and effects. Specifically, for a compound task $c$, they are a subset of the mentioned literals described in the Simple Inference section, and a super-set of the actual preconditions and effects for any given refinement and execution of a task $c$.

@@

\begin{algorithm}[h]
	\caption{Calculation of linearized methods}
	\label{alg:Algorithm1}
	\KwData{$(F, T_P, T_C, \delta, M)$}
	\KwResult{$(F, T_P, T_C, \delta, M)$}

	\For {$m=(t, (T_m, \singlePrec, \alpha)) \in M$} 
	{
		\tcc{An edge $(t, t')$ in $G$ means $t$ is ordered before $t'$}  
		$G \gets \singlePrec$ \\
		\label{alg:StartBuildGraph}
		\For{a $\in$ F}{  
			\For{$t \in T_m$}{
				\For{$t' \in T_m$}{
					if $a \in \AddS(t)$ and $a \in \PreS(t')$, add $(t, t')$ to $G$  \\ 
					if $a \in \AddS(t)$ and $a \in \DelS(t')$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \PreS(t')$, add $(t', t)$ to $G$  \\ 
					if $a \in \DelS(t)$ and $a \in \AddS(t')$, add $(t, t')$ to $G$ \\  
				}
			} 
			\label{alg:EndBuildGraph}	
		}	
		\label{alg:StartCycleBreak}
		\While{$G$ has cycles in it}{
			Delete a random ordering in $G$ that is not in $\singlePrec$ \\   % $\PreS, \DelS, \AddS$, rather than $prec$ \;
		}
		\label{alg:EndCycleBreak}
		$\prec'$ = Any linearization of $G$ \\
		\label{alg:TopSort}
		$m' = (tasks(m), \prec', \alpha(t))$ \\
		$M' = M' \cup  \{m'\}$ \\

	}
	\Return $D' = (F, T_P, T_C, \delta, M')$ \\
\end{algorithm}

@@

 \begin{figure}[h]
 	\caption{Example of Desired Additional Orderings}
 	\label{fig:OrderingRules}
	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{Del}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{first}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em ,
					body = {right = 4em of Del} 
			};

@@

	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{Del}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em
				%body = {below left = 2em and 2em of } 
			};

			\action{Prec}{SinglePrec,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of Del} 
			};

			\action{Add}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of Prec} 
		};

			\path[every node/.style={font=\sffamily\small}]
			(Prec) edge [->,bend right] node [left]  {} (Del);
			\end{tikzpicture}
			\caption{C deletes a fact in preconditions of A  -- so A before C}	
		\end{subfigure}
	}

	\scalebox{0.75}{
		\begin{subfigure}{7cm} 
			\begin{tikzpicture}[auto,node distance=1.2cm,
			thick,main node/.style={circle,draw,font=\sffamily\Large\bfseries},
			square effect/.style={rectangle,draw,font=\sffamily\Large\bfseries}]

			\action{Add}{SingleAdd,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em 
			};

			\action{Prec}{SinglePrec,
			width  = 2.5em, 
			height = 2.5em, 
			pre length = 1em,
			eff length = 1em,
			body = {left = 4em of Add} 
			};

			\action{Del}{SingleDelete,
				width  = 2.5em, 
				height = 2.5em, 
				pre length = 1em,
				eff length = 1em,
				body = {left = 4em of Prec} 
			};

			\path[every node/.style={font=\sffamily\small}]
			(Del) edge [->, bend right] node [left]  {} (Add);
			\end{tikzpicture}
			\caption{B adds a fact that C deletes -- so C before B}
		\end{subfigure}
	} 
\end{figure}

@@

We test the $panda_{\pi}$ solver by \cite{useClassicalHuristicICAPS18,useClassicalHeuristicIJCAI19,progressionsearchJAIR20} on both the original and the linearized problems. According to \cite{holler2021loop} the best setting for solving partial-order problems is \textit{GA* FF th+gi}, and the best setting for total-order is \textit{GBFS Add th+s}. 
Both turn the problem into a classical planning problem (in RC model). The former uses weighted A* search \todo{confirm weight}, the FF heuristic by \cite{FF}, and visited lists.  The latter uses Greedy best first search, Add heuristic by \cite{Add}, and visited lists.

Hashing is used to speed up checks to the visited list. Both approaches use \textit{th}, i.e. uses task hash approximation (computes  a  hash  value  that  only  incorporates  information  on which task is how often in a given TN) to replace tests for task network isomorphism. 
For \textit{th+s} first hash with taskhash and then use the exact test on all TNs in the hash bucket.
When \textit{+gi} follows, the exact test is performed in case of a hash collision.

%incomplete: (GA* FF th)
%/pandaPIengine -H "rc2(ff)" -w 2  --noLayers --noGIcheck (GA* FF oh)
%/pandaPIengine -H "rc2(ff)" -w 2  --noLayers  (GA* FF oh+gi)

%incomplete: ./pandaPIengine -H "rc2(add)" -g "none" -Q  --noLayers   --noOrderPairs   --noGIcheck  (GBFS Add th)
%./pandaPIengine -H "rc2(add)" -g "none"  -T   --noLayers   --noOrderPairs   --noGIcheck  (GBFS Add s)
%./pandaPIengine -H "rc2(add)" -g "none"  --noLayers   --noOrderPairs  --noGIcheck  (GBFS Add th+s)

We compare the performance of panda$_\pi$ on the original problem and the pre-processed problem. The same setting is used for re-runs. For other planners, panda$_\pi$ with rc2(Add) is used for re-runs. We also test the latest version of TOHTN planners HyperTensioN and Lilotane on the transformed problems. Re-runs use panda$_{\pi}$ with the best heuristic(Add). We test both Complex and Simple Inference for linearization. Note that Complex Inference can only be inferred on grounded problems, but Lilotane and HyperTensioN are lifted planners.
